Metrics

### 2023-12-15 src/plots.Rmd
Add perf by sex plots

# Bulk calc per model based on age, physician coding stage, and cause of death
calc_by <- function(
        df,
        func,
        name = "Metric",
        by_age = TRUE,
        by_stage = TRUE,
        by_cod = TRUE,
        by_age_range = TRUE,
        ...
    ) {
    out <- list()

@@

@@

#### Cases by Age Group and Sex

@@

@@

        # Calc num and perc cases for age range
        narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
        parange <- (narange / arows) * 100
        parange_label <- if (round(parange) >= 1) round(parange) else "<1"

@@

        # Calculate num and perc cases for cod
        ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE) %>% nrow
        pcod <- (ncod / nagree) * 100
        pcod_label <- if (round(pcod) >= 1) round(pcod) else "<1"

>>>>

# Bulk calc per model based on age, physician coding stage, and cause of death
calc_by <- function(
        df,
        func,
        name = "Metric",
        by_age = TRUE,
        by_stage = TRUE,
        by_sex = TRUE,
        by_cod = TRUE,
        by_age_range = TRUE,
        ...
    ) {
    out <- list()

@@

    # Calc metric by sex for each age group
    if (by_sex) {

        # Calc metric by cod
        for (a in c("adult", "child", "neo")) {
            for (sx in c("Male", "Female")) {

                # Filter data for cod
                df_filter <- df %>% filter(
                    sex == sx & is_agreed == TRUE & age == a
                )
                metric_name <- sprintf(
                    "%s %s Sex Agree %s", name, str_to_title(a), sx
                )

@@

#### Cases by Sex and Age Group

@@

#### Sex Performance

Display a plot for each age group of performance for physician agreed records by sex.

```{r, fig.width = 6, fig.height = 2.5}
for (a in c("adult", "child", "neo")) {

    # Create label and ref for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
    aref <- str_to_title(a)

    # Get unique sex columns
    sex_col <- out %>% select(starts_with(sprintf(
            "PCCC %s Sex Agree ",
            aref
        ))) %>%
        names

    # Create sex with counts
    sex_remap <- list()
    sex_counts <- list()
    for (sx_col in sex_col) {

        # Get sex without prefix
        sx <- gsub(sprintf("PCCC %s Sex Agree ", aref), "", sx_col)

        # Calc num and perc cases for age range
        nsex <- df %>% filter(sex == sx & is_agreed == TRUE & age == a) %>% nrow
        psex <- (nsex / arows) * 100
        psex_label <- if (round(psex) >= 1) round(psex) else "<1"

        # Add label for age ranges
        sex_remap[[sx]] <- paste0(
            sprintf("%s %s", alabel, sx),
            "\n(n=", nsex, ", ", psex_label, "%)"
        )

        # Store age range count data
        sex_counts[[sx]] <- nsex
    }

    # Prepare boxplot data
    sxdata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s Sex Agree", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s Sex Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "Sex",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "Sex" = recode(Sex, !!!sex_remap)
        ) %>%
        group_by(Sex) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Mid Value" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                PCCC,
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        )

    # Create cod order based on max pccc
    sxorder <- sxdata %>%
        group_by(Sex) %>%
        summarise("PCCC Max Value" = max(PCCC, na.rm = TRUE)) %>%
        select(Sex, `PCCC Max Value`) %>%
        arrange(desc(`PCCC Max Value`)) %>%
        pull(Sex)
    sxdata$Sex <- factor(sxdata$Sex, levels = rev(sxorder))

    # Plot boxplot
    sxplot <- sxdata %>%
        ggplot(aes(x = Sex, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_point(
            aes(y = `PCCC Mid Value`),
            shape = 1,
            size = 1.5,
            fill = "white",
            color = "darkgray",
            alpha = 0.8,
            position = position_nudge(x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.09)
        ) +
        geom_text(
            aes(label = `PCCC Mid`),
            color = "#4d4d4d",
            size = 2,
            hjust = 1,
            position = position_nudge(y = -0.025, x = -0.35)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.09)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.04),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.04),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)"
        ) +
        ylim(0.1, 1) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            )
        )

    # Save the plot
    print(sxplot)
    ggsave(
        sprintf("../manuscript/fig-perf-sex-%s.pdf", a),
        plot = sxplot,
        dpi = 300
    )
}
```

@@

        # Calc num and perc cases for age range
        narange <- df %>% filter(age_range == ar & is_agreed == TRUE & age == a) %>% nrow
        parange <- (narange / arows) * 100
        parange_label <- if (round(parange) >= 1) round(parange) else "<1"

@@

        # Calculate num and perc cases for cod
        ncod <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE & age == a) %>% nrow
        pcod <- (ncod / nagree) * 100
        pcod_label <- if (round(pcod) >= 1) round(pcod) else "<1"
